---
title: "Correlation between Catholic Literacy Rates and University Applications"
author: "Ishaan Bansal"
date: '2022-02-06'
output:
  bookdown::pdf_document2:
    toc: no
abstract: "Literacy rates are a good indicator of number of university applications. We usually assume that a higher literacy rate is indicative of increased university applications. This paper will work to prove this relationship using data sourced from Open Data Toronto"
thanks: "Code and data are available at:https://github.com/ishaan-bans/CatholicSchoolLiteracy.git"
bibliography: references.bib

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("ggplot2")
install.packages("bookdown")
library(ggplot2)
library(bookdown)
```

# Introduction
Data is taken from different regions of Canada. Shows raw data for Catholic literacy rates and University applications. Using this data this paper will attempt to prove a positive correlation between Literacy rates and University Applications. 

# Data
The data is sourced from Open Data Toronto [@citeopendatatoronto]. By filtering the data I was able to select only the columns I require for this analysis - Catholic Literacy rates and Catholic University applications using dplyr [@dplyr]. I will then create a plot using tidyverse [@citetidyverse] and ggplot [@ggplot]

```{r}
### Creating Plot ###
date1 = read.csv('Raw_data.csv')
ggplot(date1, aes(x='Catholic School Literacy', y= 'Catholic University Applicants')) +
    geom_point()


```

# Conclusion
As the plot shows, there is significant presence of a strong positive relationship between Catholic Literacy rates and Catholic University Applications. This proves our initial hypothesis. 

# References
[@citeR]
[@citebookdown]